% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\topmargin = -.5in
\setlength{\textheight}{10in} 
%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\name{Christopher Rosenthal}
\address{1136B 15th Ave\\Seattle, WA 98122} 
\address{\textit{T:} (630) 788-0468\\\textit{Email:} crosenth@gmail.com}
\begin{resume}

\section{Experience}

\href{http://depts.washington.edu/labweb/}{\textbf{University of Washington Department of Laboratory Medicine}},
Seattle, Washington USA\\
\textit{Senior Bioinformatics Software Engineer} \hfill \textbf{2012 - Present}

\href{http://www.seattletimes.com/}{\textbf{The Seattle Times Company}},
Seattle, Washington USA\\
\textit{Software Engineer} \hfill \textbf{2010 - Present}
\begin{itemize} \itemsep -2pt
\item Responsible for support and scalability of software applications designed for digital technologies.
\item Optimized legacy content management code base and server infrastructure to streamline engineering development and support.
\item Successfully worked with journalists and nontechnical stakeholders in development, testing and deployment of software applications.
\end{itemize}

\href{http://www.indiana.edu/~folklore/}{\textbf{Indiana University Department of Folklore \& Ethnomusicology}}, Bloomington, Indiana USA\\
\textit{Software Engineer, \href{http://www.iub.edu/~wer/}{WER Virtual Museum project}} \hfill \textbf{2008 - 2010}
\begin{itemize} \itemsep -2pt
\item Refactored and optimized the existing web site code base.
\item Created a software environment for nontechnical professors to easily manage future updates and deliver content to a wider audience of students.
\end{itemize}

\href{http://geology.indiana.edu/}{\textbf{Indiana University Department of Geological Sciences}}, Bloomington, Indiana USA\\
\textit{Bioinformatics Software Engineer} \hfill \textbf{2008 - 2009}
\begin{itemize} \itemsep -2pt
\item Designed and implemented a first ever coral reef gene ontology algorithm to construct relationships between coral reef diseases and their environments all over the world.
\item Designed a relational database schema to facilitate the organization of coral reef data.
\item Developed a Microsoft Virtual Earth and Google Earth visualization of the disease ontology.
\end{itemize}

\href{http://www.regenstrief.org/}{\textbf{Regenstrief Institute}},
Indianapolis, Indiana USA\\
\textit{Software Engineer and Research Assistant} \hfill \textbf{2005 - 2007}
\begin{itemize} \itemsep -2pt
\item Responsible for all phases of medical research software development including the testing, designing and implementation of medical software aimed at streamlining health care and establishing a basis for the management of electronic medical records.
\item Administered projects including the \href{http://aurora.regenstrief.org/mw}{Medical Workstation (MW)}, \href{http://aurora.regenstrief.org/javasig}{Java SIG HL$_{7}$} and XSLT Web Service Framework (XWSF).  All projects were managed and developed using open source practices.  
\end{itemize}

\href{http://chem.indiana.edu/}{\textbf{Indiana University Department of Chemistry}}, Bloomington, Indiana USA\\
\textit{Software Engineer, \href{http://calm.indiana.edu/}{CALM project}} \hfill \textbf{2003 - 2005}
\begin{itemize} \itemsep -2pt
\item Developed and supported a custom content management system.
\item Created web based software learning tools for university professors, teachers and students.
\item Online course adviser for over 60 high schools and universities across the country.
\end{itemize}

\section{Education}
\href{http://www.iub.edu/}{\textbf{Indiana University}}, Bloomington, Indiana USA\\
\begin{tabular}{ p{10cm} l } 
M.S., \href{http://xavier.informatics.indiana.edu/gradsites/bio/masters/}{Bioinformatics}, 2009 & B.S., \href{http://www.cs.indiana.edu/}{Computer Science}, 2005\\
Thesis Topic: Disease Ontologies in Coral Reef Ecosystems & With Honors in Computer Science\\
Adviser: \href{http://www.informatics.indiana.edu/dalkilic/}{Professor Mehmet Dalkilic} & \href{http://www.bio.indiana.edu/}{Biology} Minor
\end{tabular}

\href{http://www.seattleu.edu/coe/}{\textbf{Seattle University}}, Seattle, Washington USA\\
Post-Baccalaureate Certificate in \href{http://www.schooloftesl.com/}{TESOL}, July 2010

\section{Computer Competencies} 
Languages: Python, Perl, Java, C\#/C++/C, Lisp, R, SQL and others\\
Databases: MySQL, Oracle, MS SQL Server, HSQL, PostgreSQL\\
Platforms: *NIX (many flavors), Mac, Windows

\end{resume}

\end{document}
